%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

	% {\textbf{\large{University of Pennsylvania CIS}} \hfill \color{darkgray}{05/2022 - Present} 
	% \\ \vspace*{2mm}
	% \color{darkgray}{\hspace*{-1mm}Research Intern} 
	% \\ 
	% \color{black}
	% \begin{minipage}{40em}
	% 	Advised by Dr. Jonathan Aldrich \& Dr. Joshua Sunshine on Gradual Verification: a state of the art verification technique that leverages partial specifications for scalability. \\
	% 	\textit{[\color{darkgray}Spring 2023\color{black}]} Developed formal proofs for establishing semantic correspondence to ensure soundness between the static and dynamic verifiers. \\
	% 	\textit{[\color{darkgray}Summer-Fall 2022\color{black}]}  Fixed optimization bugs and implemented a Property Based Testing tool for evaluating the soundness of Gradual $C_0$$.^{[3][8]}$
	% \end{minipage}}
	{\textbf{\large{Utrecht University, Advanced Functional Programming Summer School}} \hfill \color{darkgray}{07/2023} 
	\\ \vspace*{1mm}
	\color{darkgray}{\hspace*{-1mm}Lectured by Dr. Wouter Swierstra and Dr. Gabriele Keller} \hfill{Utrecht, Netherlands} 
	\\ 
	\color{black}
	\begin{minipage}{40em}
			 Participated in a mix of lectures, labs and a busy social program, discussing advanced topics regarding the \textbf{theory and practice of Haskell programming}.
	\end{minipage}}

	{\textbf{\large{Amazon, Summer Undergraduate Research Experience}} \hfill \color{darkgray}{06/2023 - 08/2023} 
	\\ \vspace*{1mm}
	\color{darkgray}{\hspace*{-1mm}Industry experience workshop led by Myles Shiroma \& Korin Torrence Johnson} \hfill{Pittsburgh, PA} 
	\\ 
	\color{black}
	\begin{minipage}{40em}
		Selected for Amazon's summer research program at Carnegie Mellon University from a pool of \textbf{$\sim$1,900 applicants}. Continued work on Gradual Verification and developed significant optimizations for asserting runtime checks in Gradual $C_0$.
	\end{minipage}}

	{\textbf{\large{Carnegie Mellon University, Software and Societal Systems}} \hfill \color{darkgray}{06/2022 - Present} 
	\\ \vspace*{1mm}
	\color{darkgray}{\hspace*{-1mm}Research Intern, advised by Dr. Jonathan Aldrich \& Dr. Joshua Sunshine} \hfill \color{darkgray}{Pittsburgh, PA} 
	\\ 
	\color{black}
	\begin{minipage}{40em}
		\color{darkgray}{\underline{Summer '23}}
		\color{black}Exploring the application of gradual verification techniques to \textbf{smart contracts} on the \textit{Algorand} blockchain platform in developing \textit{Gradually Verified Teal}.

		\color{darkgray}{\underline{Spring '23}}
		\color{black}Worked on \textbf{formal proofs} for establishing semantic correspondence to ensure soundness between the static and dynamic verifier.

		\color{darkgray}{\underline{Summer/Fall '22} }
		\color{black}Fixed optimization bugs and implemented a \textbf{Property Based Testing} tool for evaluating the soundness of Gradual $C_0$ source code.
	\end{minipage}}

	{\textbf{\large{Cornell University, Computer Architecture \& Programming Abstractions}} \hfill \color{darkgray}{10/2021 - 12/2022} 
	\\ \vspace*{1mm}
	\color{darkgray}{\hspace*{-1mm}Undergraduate Research Assistant, advised by Dr. Adrian Sampson} \hfill \color{darkgray}{Ithaca, NY}
	\\
	\color{black}
	\begin{minipage}{40em}
		\color{darkgray}{\underline{Fall '22} } 
		\color{black} Worked on a \textbf{symbolic execution} tool for verifying parallelism in Calyx.

		\color{darkgray}{\underline{Fall '21/Spring '22} }
		\color{black} Fixed compiler front-end bugs and implemented \textit{Graphicionado Graph Analytics} algorithm in Calyx.
	\end{minipage}} 

\end{rSection} 
